---
title: "linear model from Web"
author: "Melissa Sanchez"
date: "Summer 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point()
```

The y-axis is SIMS and the x-axis is ARMS. This plot shows that here is a positive linear correlation. There is a positive correlation between ARM and SIMS displayed in this plot above. 


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.68, which is a positive number that indicates the line will travel upwards towards the right. 


### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

1.226 if you go up or down that is the prediction interval. 

In this linear regression model, the numbers that should be considered to create the predication equation are the estimate coefficients. To predict SITS based on ARM strength, the intercept, -4.1 would be added to 0.5, ARM and then multiplied by ARM.  The evaluation for the line that fits this is SIMS is equal to -4.1 + .05 *ARM. The formula needed is y= mx  + b to create the line. The bigger the adjusted R-squared, the better the model. The degree of freedom will be taken away from the Multiple-R Square and then what would be left is the Adjusted R-squared. The 145 degree of freedom is how many data points are displayed in the plot. The line is to be estimate where it hits the y-axis. Each data will change the degree of freedom. 

The 145 degree of freedom is how many data points are displayed in the plot. The line is to be estimated where it hits the y-axis. Each data will change the degree of freedom. Every time you add more stuff to the model, the multiply r-squared will go down a small percentage. 


#### Predict at target point

```{r}
newdata = data.frame(GRIP= 94, ARM = 88)
predict(model.1, newdata, interval = "prediction", level = .99)
```

This is a prediction interval. How far does one point vary from the other if you take .7 away from 3.13, you would end up approximately 2.3


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2







